\documentclass[10pt]{article}


\usepackage{amssymb,amsthm,amsmath}
\usepackage{enumerate}
\usepackage{graphicx,color}
\usepackage[hidelinks]{hyperref}
%\usepackage{refcheck}

\newcommand{\dd}{\mathrm{d}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\1}{\textbf{1}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}} 
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\p}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\scal}[2]{\left\langle #1, #2 \right\rangle}
\newcommand{\red}{\color{red}}
\newcommand{\shift}{\vdash}
\newcommand{\lL}{\mathcal{L}}

\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\sgn}{sgn}

\usepackage[paper=a4paper, left=1.3in, right=1.3in, top=1in, bottom=1in]{geometry}
\linespread{1.3}
\pagestyle{plain}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}


\newtheorem{conjecture}{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[theorem]{Definition}
\newtheorem{exmp}[theorem]{Example}





\begin{document}

\section{Notes on Deep Partial Differential Equations}

\subsection{The Deep Galerkin Method}

Drawbacks of grid methods

Numerical methods based on grids often fail when dimensionality becomes too large. (b/c grid points exponential in dimension). Stabiliy also much huge mesh sizes

Advantages of DGM

Mesh free. 

?Computational graph? 

Training Method:

Randomly sample points from region where function defined

?Why do expect having a good fit on the boundary to be a good fit inside?
	If harmonic then this makes sense. Maybe work for good class of PDEs?

Mathematical Formulation:

We define $f(t,x;\theta)$ with parameter $\theta$(fitting parameter)  - actually these are given by neural network

?How do we compute differential operator loss?
-Because we have f approximation defiend everywhere

$\nu$ term is density, describes mass of space. Distribution of space

Approximation works for class of quasilinear parabolic PDE
2018 Sirignano and Spiliopoulos *should look into this*

Implmentation Details:

DGM layers: input - hidden ... hidden - output
	Takes as input original x and input from previous layer

?Highway network?

Drawbacks:

**Number of parameters in each hidden layer of DGm is roughly eight times bigger than same number in usual dense layer

Second orders derivatives quadratically costly: Could use backprop but instead use finite differenc scheme

?Numerous choices made outlined in 47 toronto?




\subsection{Comparisons}

runge ketta?

\subsection{Ideas}

Approximate other functions? Ray tracing equation?

\subsection{Questions}

Where does the parallelism come in?

\begin{thebibliography}{9}



\end{thebibliography}

\end{document}



